Data Preparation

### 2019-03-14 Data Preparation.Rmd
remove missing value from textual data

    # Remove words occuring once or twice in corpus (usually names, website links or typos)
    add_count(word) %>%
    filter(n > 2) %>%
    select(-n)

>>>>

    # Remove words occuring once or twice in corpus (usually names, website links or typos)
    add_count(word) %>%
    filter(n > 2) %>%
    select(-n) %>%

    # remove NA
    filter(!is.na(word))
